---
title: "Proposal"
author: "ZEKUN WANG,JINWEN XU,YUMAN WU,YIDAN HUO,YICHENG DU"
date: "2023-11-5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.**Including code to read data**

```{r, results='asis'}
library(htmltools)
library(kableExtra)
data <- read.table("amazon_reviews_us_Musical_Instruments_v1_00.tsv", header = TRUE, sep = "\t", fill = TRUE)
selected_data <- head(data)

kable(selected_data, "html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                font_size = 12) %>%
  scroll_box(width = "750px", height = "500px")
```


2.**Descriptions of the variables:**

We selected the Amazon US Customer Reviews Dataset from Kaggle, which has a total size of 54.41GB. This dataset contains 37 distinct folders, corresponding to different product categories. Each folder includes 15 variables such as 'star_rating'， 'customer_id'，and so on. For our analysis, we focused on two specific variables: 'star_rating' and 'review_date'.The specific variable explanations are as follows:

(1)Star_rating” is the 1-5 star rating of the review. Its data type is int.
(2)“Review_date” is the date when the review is published. Its data type is datetime.


3.**Question**:

**3.1**  How can we create new variables that capture the full information of a time series for further effective analysis?

**3.2** How can we know the 5 fields with the best development and the 5 fields with the worst development in recent years?

4.**Statistical methods**

**4.1**:

   Covariance function of a time series\[ \Gamma(m)=[\gamma(0),\gamma(1)...,\gamma(m)]\]. The covariance function is a function of the covariance between two random variables and can reveal the correlation of the random variables at different points in time.
The sample autocovariance function of \[\{x_1,x_2,...,x_n\} \]is defined as:
\[ \gamma(h)=n^{-1}\sum_{j=1}^{n-h}(x_{j+h}-\bar{x})(x_{j}-\bar{x}),0 \leq h<n\] where \( \bar{x} \) is the mean of \( x_i \) .

**Computational steps**:
Calculate the sample covariance function: 
(1)Calculate the mean of the sequence. 
(2)For each possible lag value, compute the covariance between the lagged sequence and the original sequence. 
(3)Use these covariances as estimates for the autocovariance function.

**4.2**: Calculate the average rating for different product categories and sort them. Determine the top five hottest product categories on Amazon, as well as the five least hottest categories.





